Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Add TBD
Move "reusable specs" to BCP

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reusable pieces of specification}

>>>>

\begin{quote}
    TBD: Section -> section
\end{quote}

@@

\begin{quote}
    TBD: in this section we:
    \begin{itemize}
        \item We show how to do BDD in Haskell
        \item How to reuse pieces of specification
        \item How to use Doctest and Hspec with Cabal's test feature
    \end{itemize}
\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reusable pieces of specification}
\label{sec:reusable-specs}

@@

\begin{itemize}
    \item
        In section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}
